\pkg{DNest4}: Diffusive Nested Sampling in \proglang{C++} and \proglang{Python}

### 2016-05-11 paper/ms.tex
Talking about the class

Running \pkg{DNest4} on this problem requires a class, which we call
{\tt StraightLine}, which has the following member functions:
\begin{enumerate}[(i)]
\item \code{void from\_prior(DNest4::RNG\& rng)}, which generates parameter
        values from the prior;
\item \code{double perturb(DNest4::RNG\& rng)}, which proposes a
        change to the parameter values, and returns $\ln(H)$ as defined in
        Equation~\ref{eqn:log_hastings};
\item \code{double log\_likelihood() const}, which evaluates the log of
        the likelihood function;
\item \code{void print(std::ostream\& out) const}, which prints parameters of
        interest to the given output stream; and
\item \code{std::string description() const}, which returns a \proglang{C++}
        string naming the parameters printed by \code{print(std::ostream\&) const}.
\end{enumerate}

>>>>

To run \pkg{DNest4} on any particular problem, such as this linear regression
example, the user needs to define a \proglang{C++} class to specify the
model. Specifically, an object of the class represents a point in the
model's parameter space. Member functions are defined which generate
the object's parameters from the prior, make proposal steps, evaluate the
likelihood, and so on. The sampler calls these member functions while
executing a run.

For the simple linear regression example, we will call the class
{\tt StraightLine}. The member variables representing the
unknown parameters are defined in the header file {\tt StraightLine.h}:

\begin{CodeChunk}
\begin{CodeInput}
class StraightLine
{
    private:
        double m, b, sigma;
};
\end{CodeInput}
\end{CodeChunk}

 which has the following member functions:
\begin{enumerate}[(i)]
\item \code{void from\_prior(DNest4::RNG\& rng)}, which generates parameter
        values from the prior;
\item \code{double perturb(DNest4::RNG\& rng)}, which proposes a
        change to the parameter values, and returns $\ln(H)$ as defined in
        Equation~\ref{eqn:log_hastings};
\item \code{double log\_likelihood() const}, which evaluates the log of
        the likelihood function;
\item \code{void print(std::ostream\& out) const}, which prints parameters of
        interest to the given output stream; and
\item \code{std::string description() const}, which returns a \proglang{C++}
        string naming the parameters printed by \code{print(std::ostream\&) const}.
\end{enumerate}
